---
title: "Week 5 - Class Coding"
author: "Samantha-Jo Caetano"
date: "Oct 13, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In your Assignment 1 you will need to grab some data from the Toronto Open Data Portal. 

Let's work together to grab a data set and perform a small (Bayesian?) regression analysis on it.

# Grabbing some Data

Here is a "user-friendly" website to get to know about the data in the Toronto Open Data portal: [https://open.toronto.ca/](https://open.toronto.ca/). Let's take a look at it. Note, if you click **Data Catalogue** at the top left-ish of the page, you should be able to see all the data available.


I am going to look at the "BodySafe" data set which looks at whether establishments offering hairstyling or barbering services were required to get a PSS licence and post their inspection notices at or near the entrance of the business. (Here is a link to this data: [https://open.toronto.ca/dataset/bodysafe/](https://open.toronto.ca/dataset/bodysafe/))

Okay, let's load in the data here:
```{r}
#install.packages("opendatatoronto")
library(opendatatoronto)
library(tidyverse)

# browse_portal()  # to look at the Open Toronto Data Portal

```

Now, if we specifically want the BodySafe data set, we can use the following process to grab it:

```{r}

search_packages("BodySafe")
# This is convenient because it gives us the identifying information
# of the BodySafe data set. Let’s pull the id from it:

search_packages("BodySafe")  
# Good, but let's save the id (I am just copying it below based off the output)


```

Alrighty, so we have saved the ID, now let's do a sanity check to make sure we are grabbing the correct data:

```{r}


```

Now, we have the ID of the data so we can grab the data itself:

```{r}



```

YAY!

# Regression Analysis

Let's perform a basic logistic regression analysis. If we use a Bayesian approach we need brms:

```{r}
# install.packages("brms")
# install.packages("rstan")
```

```{r}
library(brms)
library(tidyverse)
```

Let's to look at the relationship between inspStatusDesc (y) and servTypeDesc (x1) and latitude (x2). Let's clean the data a bit and do some sanity checks first: 

```{r}


```


*Please Note: This is not really an appropriate analysis, especially from a "practical" perspective. It is only being used here for demonstrative purposes!*


```{r}



```
